\documentclass{article}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{caption}
\usepackage[utf8]{inputenc}
  \usepackage[
    backend=biber,
    style=ieee,
  ]{biblatex}
 


\title{CS6000 - Fourth Assignment}
\author{Marc Moreno Lopez}
\date{September 25th 2018}

\begin{document}

\maketitle

\section{Report}

%Describe your learning/process so far on the survey paper.  I expect this to be short. 

For the draft we have decided to extract some information about each paper. This information won't go on to the final version of the paper. It was just a way for us to organize and group all the different papers. It is also a good way of seeing things that they have in common so that we can extract that information and later use it to write about those papers. 

Thus far, we have identified approximately 60 papers, including survey papers for segmentation based on supervised learning and recent papers for unsupervised segmentation. The majority of the papers pertain to medical images. While this, in itself, is not problematic, we will endeavor to separate unsupervised segmentation methods that are closely tailored to medical imagery from those that are more generally applicable. The three "axes" of our survey will be supervised learning, unsupervised learning and hybrid approaches. The hybrid approaches generally combine supervised learning with unsupervised learning so the three axes are not really orthogonal (they may not even be three dimensional!) but we believe this is a reasonable way to organize our data.

Inside my repo I have cloned the overleaf project. In this folder you can find all the files for the tex file.




\end{document}
